---
title: "Climate change will outdate the European Union fishereis quota allocation"
author: "Alex Tidd, <sup>1</sup> Elena Ojea <sup>1</sup>, Juliano Palacios-Abrantes<sup>2</sup>, William W. L. Cheung ?, U. Rashid Sumaila ?"
date: `r date()`
# output: html_notebook
---

```{r setup, include=FALSE, results = 'hide'}

#### READ ME !!! ####
library(MyFunctions)

#### Library ####
packages <- c(
  # "readxl", # Read dataframe
  # "data.table", # Read dataframe (Fast!)
  # "wesanderson",
  "tidyverse", # for all data wrangling and ggplot
  "here",
  "janitor",#, # for data cleaning
  # "tidytext", # to order the facet wrap https://juliasilge.com/blog/reorder-within/
  # "cowplot", # for figures 1 and 3
  # "ggimage", #for reading images to the circular plot
  # "ggrepel", # for nice plot labels
  # "ggsflabel", # for nice sf_plots labels
  # "spdep", # for poly2nb old
  "sf", #Spatial analysis
  "sp", #Spatial analysis
  # "purrr",#Spatial analysis
  # "rgdal", #Spatial analysis
  "tools", #Spatial analysis
  # "parallel", # for parallelization
  # "taxize", # For getting species names
  # "rfishbase", # for species ecosystem affinity
  # "zoo", #for runing mean
  # "pgirmess" # for dune test after kurtis wallas
  "knitr"
)

my_lib(packages)

# Fix new updates of sf package
sf::sf_use_s2(use_s2 = FALSE)

# data_path <- "../data"
data_path <- my_path("D")
```

# Methods

## Species selection

In here we take the EU list of species and filter out those that we have data for to project under climate change.

Our analysis included 79.48% (n = 62) of the taxa reported at the species level by the European Union (n = 78).

```{r species_selection, eval = F, echo = F}
# -------------------- #
# Data needed
# -------------------- #

# Load TAC species list
Tac_spp_list <- my_path("D","Tacs", name = "eu_tacs_2020_lookup.csv", read = T) %>% 
# Eu_spp_list <- read.csv(here("data/species/eu_species.csv")) %>% 
  clean_names() %>% 
  rename(taxon_name = scientific_name) %>% 
  select(-common_name)

# Load EU species list
Eu_spp_list <- my_path("D","Species", name = "eu_species.csv", read = T) %>% 
# Eu_spp_list <- read.csv(here("data/species/eu_species.csv")) %>% 
  clean_names() %>% 
  rename(taxon_name = scientific_name) %>% 
  select(-common_name) %>% 
  filter(alpha_3_code %in% Tac_spp_list$species)

# Load SAU species list
Sau_spp_list <- my_path("G","SAU", name = "exploited_species_list.csv", read = T) %>% 
# Sau_spp_list <- read.csv(here("data/species/exploited_species_list.csv")) %>% 
  clean_names()

# -------------------- #
# Get Species lists
# -------------------- #

# Get species list to analyze (n = 62)
Project_spp <- Eu_spp_list %>% 
  left_join(Sau_spp_list,
            by = "taxon_name") %>% 
  filter(!is.na(taxon_key))

# Percentage of total taxa
nrow(Project_spp)/nrow(Eu_spp_list)*100 # 80% of the taxon reported

# Save data for future
write_csv(Project_spp,
          my_path("D","Species","species_analyzed.csv"))

Project_spp
```

### Who was left out (n = 6)

```{r species_selection, eval = F, echo = F}

Eu_spp_list %>% 
  anti_join(Project_spp,
            by = "taxon_name")
```


## Spatial analysis

### Crop out european region

In the following analysis we will crop out the EU region to a 0.5 x 0.5 grid

### Data for spatial

#### shapefiles

- **EU shaopefile.** This shapefile covers the EU ICES areas. It was provided by Elena

- **North Africa shapefile** This shapefile covers the Morocco Coastal (Division 34.1.1 of FAO Major Area 34) and its breakdown. It was provided by FAO. http://www.fao.org/fishery/geonetwork/srv/eng/catalog.search#/metadata/fao-fsa-nested-map-34.1.1

```{r spatial_data_crop, eval = F, echo = F}

## EU Shapefile

Eu_shp <- st_read(my_path("D","Spatial/ices_areas","ICES_Areas_20160601_dense.shp")) %>% 
  st_simplify(preserveTopology = TRUE, dTolerance = 0.01) %>% 
  clean_names() %>% 
  select(sub_area,division,sub_division = sub_divisio,geometry)

# eu_map <- ggplot(Eu_shp) +
  # geom_sf(aes(fill = as.character(sub_area)))

# ggsave(my_path("D","Spatial/ices_areas","eu_map.png"),
       # eu_map)

# SAU/DBEM Gridcell
Eez_cell_id <- my_path("G","Spatial/DBEM/","EEZ_CellID.csv", read = T)

# Load Gridcell
Lon_lat_grid <- my_path("G", "Spatial/DBEM","Lon_Lat_DBEM.txt", read = T, header = F)
colnames(Lon_lat_grid) <- c("index","lon","lat")


## North Africa Shapefile

na_shp <- st_read(my_path("D","Spatial/FSA-NESTED_34-1-1","FSA-NESTED_34-1-1.shp")) %>% 
  st_simplify(preserveTopology = TRUE, dTolerance = 0.01) %>% 
  select(sub_area = F_SUBAREA,division = F_AREA,sub_division = F_SUBDIVIS,geometry)

# na_map <- ggplot(na_shp) +
#   geom_sf(aes(fill = as.character(ID)))

 
# ggsave(my_path("D","Spatial/FSA-NESTED_34-1-1","na_map.png"),
#        na_map)

```

#### Combine shapefiles


```{r north_africa_sf, eval = F, echo = F}


complete_map <- rbind(na_shp,Eu_shp)

write_sf(complete_map, my_path("D","Spatial/project_sf","project_sf.shp"))

reg_map <- ggplot() +
  geom_sf(data = complete_map, aes(fill = sub_area)) #+
  # geom_sf(data = na_shp, aes())


# ggsave(my_path("D","Spatial","reg_map.png"),
#        reg_map)

```


### Spatial croping

```{r species_selection, eval = F, echo = F}

# Convert DBEM gridcell to sf
Grid_sf = st_as_sf(Lon_lat_grid,
            coords = c("lon", "lat")
            ) %>% 
 st_set_crs(4326) %>% # to match shapefiles
 st_transform(4326) # to match shapefiles

# head(Grid_sf)

# Merge grid sf and EU sf
Eu_grid <- complete_map %>% 
  st_join(Grid_sf, join = st_contains) %>% 
 filter(!is.na(index)) %>%
 arrange(index) 

# Merged correctly?
# head(Eu_grid)

# Transform sf to df
Eu_grid_df <- as.data.frame(Eu_grid) %>% 
 select(index,sub_area:sub_division)


# Double check grid makes sense
Eu_grid_df %>% 
  left_join(Lon_lat_grid) %>% 
  ggplot() +
  geom_tile(aes(
    x = lon,
    y = lat,
    fill = as.factor(sub_area),
    color = as.factor(sub_area)
  )
  )


# Save data
write_csv(Eu_grid_df,
          my_path("D","Spatial","eu_grid.csv"))

### TO show in notebook

my_path("D","Spatial","eu_grid.csv", read = T) %>% 
  left_join(Lon_lat_grid) %>% 
  ggplot() +
  geom_tile(aes(
    x = lon,
    y = lat,
    fill = as.factor(division),
    color = as.factor(division)
  )
  )

```


## Potential Results

Right now doing analysis at the species level

## Speices-area subset

- Mackerel scombrus scombrus 8c_9_10_cefcaf (the north sea has been done too much and this is important for spain)
- Anglers Lophidae ANF_7 – Anglers have high price and important on west coast
- Hake Merluccius merluccius HKE_5b_6_7_12_14
- Herring Clupea harengus HER_2ª_4_7D ( Pleagic on the move and important as there was a collapse in north sea in70s)
- Melanogrammus aeglefinus Haddock HAD_6B_12_14 (UK have big interest in this)
- Gadus morhua Cod  COD7XAD34 (codo n western side of atlantic rather thn north sea important for iireland etc..
- Sole solea Sole SOL_2ª_4 (sole important for the dutch.. highest price in eu)
- Anchovy ANE_8 (very important)

### Read DBEM data

```{r dbem_data, eval = T, echo = T}


eu_grid <- my_path("D","Spatial","eu_grid.csv", read = T) %>% 
  distinct(index,sub_area,division,.keep_all = T)

# taxon <- 601278
# esm = "GFDL85"

read_dbem <- function(taxon,esm){
  
  file_name <- paste0(taxon,"MCP.RData")
  esm_name <- paste0("cimip6/DBEM_outputs/C6",esm,"F1_t2")
  read_me <- my_path("G",esm_name, name = file_name)
  
  if(file.exists(read_me) == F){
    print("no data for that spp. Bruh!")
    data <- data.frame()
  }else{
    
    load(read_me)
    
    colnames(sppMCPfnl) <- seq(1951,2100,1)
    
    data <- sppMCPfnl %>% 
      as.data.frame() %>% 
      rowid_to_column("index") %>% 
      gather("year","mcp",2:151) %>% 
      left_join(eu_grid,
                by = "index") %>% 
      mutate(remove_me = ifelse(is.na(sub_area) & is.na(division) & is.na(sub_division), "yes","no")) %>% 
      filter(remove_me == "yes") %>% 
      mutate(taxon = taxon,
             esm = esm,
             rcp = ifelse(str_detect(esm_name,"85"),"rcp85","rcp26")
             ) %>% 
      group_by(sub_area,division,year,taxon,esm,rcp) %>% 
      summarise(div_mcp = sum(mcp, na.rm= T),
                .groups = "drop")
  }
  
  return(data)
  
}


```


#### Load data

Shiny app https://clock-espana.shinyapps.io/EUTAC/

Cod COD_2A_3A_4 UK  approximately 40 % of TAC and political
Horse mackerel JAX_9 Biggest TAC Portugal worth over 70% of revenue
Plaice 2A_4 Important economically for DEN approx. 20% TAC and overall plaice contributes to 20% of total fish revenue



```{r}


exploited_spp <- my_path("G","SAU","exploited_species_list.csv",read = T)

# Results exploration using these stocks
test_stocks <-
  data.frame(
  taxon = c(
    rep(600118,5), # mackrel 8C_9_10
    rep(600030,15), #hake HKE_5b_6_7_12_14
    rep(600024,5), # herring HER_2ª_4_7D 
    rep(601381,7), # hadock HAD_6B_12_14
    rep(600069,15), # Cod COD7XAD34
    rep(600525,2), # Solea SOL_2ª_4
    rep(600066,5), # anchovy ANE_8 economically for spain 10% revenue and 30tonne TAC
    rep(601278,2), # Horse mackerel JAX_9 Biggest TAC Portugal worth over 70% of revenue
    rep(600069, 5), # Cod COD_2A_3A_4 UK  approximately 40 % of TAC and political
    rep(601342,4)# Plaice 2A_4 Important economically for DEN approx. 20% TAC and overall plaice contributes to 20% of total fish revenue
          ),
  stock = c(
    rep("MAC_8C_9_10",5), # mackerel 8C_9_10
    rep("HKE_5b_6_7_12_14",15), #hake HKE_5b_6_7_12_14
    rep("HER_2ª_4_7D",5), # herring HER_2ª_4_7D 
    rep("HAD_6B_12_14",7), # haddock HAD_6B_12_14
    rep("COD7XAD34",15), # Cod COD7XAD34
    rep("SOL_2ª_4",2), # Solea SOL_2ª_4
    rep("ANE_8",5), # anchovy ANE_8 economically for spain 10% revenue and 30tonne TAC
    rep("JAX_9",2), # Horse mackerel JAX_9 Biggest TAC Portugal worth over 70% of revenue
    rep("COD_2A_3A_4", 5), # Cod COD_2A_3A_4 UK  approximately 40 % of TAC and political
    rep("PLA_2A_4",4)# Plaice 2A_4 Important economically for DEN approx. 20% TAC and overall plaice contributes to 20% of total fish revenue
  ),
  sub_area = c(
    8,9,9,10,34.1, #mac
    c(5,6,6,rep(7,8),rep(12,3),14), # hake
    2,4,4,4,7, # herr
    c(6,rep(12,3),rep(14,3)), #had
    c(rep(7,7),rep(8,4),9,9,10,4.1), # Cod
    c(2,4), #Sol
    rep(8,5), # ancho
    rep(9,2), # horse mackerel
    c(2,3,4,4,4), # cod 
    c(2,3,3,3) #Plaice
    ),
  division = c(
    c("c","a","b","a",4.1),
    c("b","a","b",letters[1:8],letters[1:3],"b"), # hake 
    c("a","a","b","c","d"), # herr
    c("b",letters[1:3],letters[1:3]), # had
    c(letters[2:8],letters[1:4],"a","b","a",4.1), # cod 
    c(NA,NA), # sol
    letters[1:5], #ancho
    c("a","b"), # horse mackerel
    c("a","a","a","b","c"), #cod 
    c("a","a","b","c") # Plaice
  )
  )

# Species list
project_spp <- my_path("D","Species","species_analyzed.csv", read = T) %>% 
  filter(taxon_key %in% test_stocks$taxon)



# DBEM results for one spp
# spp_data <- read_dbem(taxon = project_spp$taxon_key[1],esm = "GFDL26")

esms <- c("GFDL26","GFDL85","IPSL26","IPSL85","MPI26","MPI85","UKESM26","UKESM85","CNRM85","CNRM26")

# DBEM results for multiple spp

tet <- function(x){
   
spp_data <- bind_rows(
  lapply(project_spp$taxon_key, read_dbem, esm = x)
) %>% 
  filter(!is.na(sub_area))

}

 # x <- tet(esms[1])
 
spp_data <- bind_rows(lapply(esms[1:2], tet))

write_csv(spp_data,my_path("R",name = "spp_dbem_data.csv"))


# Lon lat DBEM
Lon_lat_grid <- my_path("G", "Spatial/DBEM","Lon_Lat_DBEM.txt", read = T, header = F)
colnames(Lon_lat_grid) <- c("index","lon","lat")

# Load project's sf
project_shp <- st_read(my_path("D","Spatial/project_sf","project_sf.shp")) %>% 
  rename(division = divisin)


# Subset data for specific stocks/regions

stock_data <- spp_data %>%
  right_join(test_stocks,
            by = c("taxon","sub_area","division")) 


# Check for NAs

stock_data %>% 
  filter(is.na(div_mcp)) %>% 
  View()

```

#### Spatial summaries

```{r}

stock_data %>% 
  left_join(eu_grid) %>% 
  group_by(sub_area,division) %>% 
  summarise(
    n_grids = length(unique(index)),
    km2 = n_grids*25
  ) %>% 
  DT::datatable(filter = 'top')

```


#### Change Relative to present

In this part we estimate the change by mid and end of the century in the region relative to the present day

```{r temporal_cahnge, eval = T, echo = F}

  
temporal_df <- stock_data %>%
  # left_join(eu_grid) %>%
  # group_by(division,year,taxon) %>% 
  # summarise(div_mcp = sum(mcp, na.rm= T)) %>% 
  mutate(
    period = ifelse(year %in% seq(1973,1978,1),"A_early",
                    ifelse(year %in% seq(2020,2040,1),"AA_med",
                           ifelse(year %in% seq(2080,2100,1),"AAA_end",
                                  NA
                           )
                    )
    )
  ) %>% 
  filter(!is.na(period)) %>% 
  group_by(division,taxon, period) %>% 
  summarise(mean_mcp = mean(div_mcp,na.rm = T)) %>% 
  spread(period,mean_mcp) %>% 
  gather("future","mcp",AA_med:AAA_end) %>% 
  mutate(per_chg = ifelse(A_early == 0 & mcp == 0, 0, # If for no change than 0
                          ifelse(A_early == 0 & mcp > 0, 100, # If changes from 0 to anything then 100
                                 # NA
                                 ((mcp-A_early)/((mcp+A_early)/2))*100 # Estimate percentage change
                          )
  ),
  plot_per_change = ifelse(per_chg > 100,100,
                           ifelse(per_chg < -100,-100,
                                  per_chg)
  )
  )
  

head(temporal_df,20)

```

```{r}

temp_map <- project_shp %>% 
  left_join(temporal_df) %>% 
  ggplot() +
  geom_sf(
    aes(
      fill = plot_per_change
    )
  ) +
  facet_wrap(~future, nrow = 1)+
  scale_fill_gradient2() +
  scale_color_gradient2()


ggsave(my_path("R","partial","temporal_map.png"),
       temp_map,
       width = 12)

```


#### Regional Estimations

```{r}

total_spp <- stock_data %>% 
  filter(!is.na(division)) %>% 
  group_by(year,taxon,stock) %>% 
  summarise(total_mcp = sum(div_mcp,na.rm=T))
  
  
regional_df <- stock_data %>%
  filter(!is.na(division)) %>% 
  left_join(total_spp,
            by = c("year","taxon","stock")
            ) %>% 
  mutate(
    per = (div_mcp/total_mcp)*100,
    sub_a_div = paste(sub_area,division,sep = ".")
  ) %>% 
  group_by(sub_a_div,stock) %>% 
  mutate(RMean = zoo::rollmean(x = per, 
                            10, 
                            align = "left", 
                            fill = NA,
                            na.rm=T)
    )


head(regional_df,20)

```

### Historical trends (area plot) by stock

```{r}
regional_df %>% 
  filter(year >= 1960) %>% 
 ggplot() +
  geom_area(
    aes(
      x = as.numeric(year),
      y = RMean,
      fill = sub_a_div
      )
  ) +
  geom_vline(xintercept = 1973) +
  viridis::scale_fill_viridis(discrete = T) +
  facet_wrap(~stock,
             ncol = 3,
             scale = "free")


ggsave(my_path("R","partial","historic_pro_stock.png"),
       last_plot(),
       width = 12)

```

### Historical trends (area plot) by sub divission 

```{r}
regional_df %>% 
  filter(year >= 1960,
         per > 0,
         !is.na(per)
         ) %>% 
 ggplot() +
  geom_area(
    aes(
      x = as.numeric(year),
      y = per,
      fill = stock
      )
  ) +
  geom_vline(xintercept = 1973) +
  viridis::scale_fill_viridis(discrete = T) +
  facet_wrap(~sub_a_div,
             # ncol = 3,
             scale = "free")


ggsave(my_path("R","partial","historic_prop_sub_div_rmean.png"),
       last_plot(),
       width = 12)

```


### Historical line (area)

```{r}

regional_df %>% 
filter(year >= 1960,
         RMean > 0,
         !is.na(RMean)
         ) %>% 
 ggplot() +
  geom_line(
    aes(
      x = as.numeric(year),
      y = RMean,
      color = sub_a_div
      )
  ) +
  geom_vline(xintercept = 1973) +
  viridis::scale_color_viridis(discrete = T) +
  facet_wrap(~stock,
             ncol = 3,
             scale = "free")


ggsave(my_path("R","partial","historic_proportion_line_rmean.png"),
       last_plot(),
       width = 12)

```

### Relative change


```{r changeline, eval = T, echo = F}

reference <- regional_df %>% 
  filter(year >= 1973 & year <= 1978) %>% 
  # View()
  group_by(sub_a_div,taxon,stock) %>% 
  summarise(ref_mcp = mean(per,na.rm = T))


relative_chng <- regional_df %>% 
  filter(year >= 1978) %>%
  left_join(reference,
            by = c("taxon", "stock", "sub_a_div")
            ) %>% 
  # View()
  mutate(per_chg = ifelse(per == 0 & ref_mcp == 0, 0, # If for no change than 0
                        ifelse(per == 0 & ref_mcp > 0, 1, # If changes from 0 to anything then 100
                               ifelse(per > 0 & ref_mcp == 0, 1, # if there was no orginially and then it
                               ((ref_mcp-per)/abs(ref_mcp))*100
                        )
                        )
            )
  ) #%>% 
  # mutate(
  #   per_chg = ifelse(per_chg > 100,100,
  #                    ifelse(per_chg < -100,-100,per_chg)
  # )
  # )


relative_chng %>% 
  # filter(taxon == 600030) %>% 
  # View()
ggplot() +
  geom_line(
    aes(
      x = as.numeric(year),
      y = per_chg,
      color = sub_a_div
      )
  ) +
  geom_hline(yintercept = 1) +
  viridis::scale_color_viridis(discrete = T) +
  facet_wrap(~taxon,
             ncol = 3,
             scales = "free")


# plotly::ggplotly(p)

p
```

### Relative change (Run 10)

```{r}

relative_chng <- regional_df %>% 
  filter(year >= 1978) %>% 
  left_join(reference) %>% 
  mutate(per_chg = ifelse(per == 0 & ref_mcp == 0, 0, # If for no change than 0
                        ifelse(per == 0 & ref_mcp > 0, 1, # If changes from 0 to anything then 100
                               ifelse(per > 0 & ref_mcp == 0, 1, # if there was no orginially and then it
                               ((ref_mcp-per)/abs(ref_mcp))*100
                        )
                        )
            )
  ) %>% 
  group_by(sub_a_div,taxon) %>% 
  mutate(RMean = zoo::rollmean(x = per_chg, 
                            10,
                            fill = "left",
                            na.rm=T)
    )


ggplot(relative_chng) +
  geom_line(
    aes(
      x = as.numeric(year),
      y = RMean,
      color = sub_a_div
      )
  ) +
  geom_hline(yintercept = 1) +
  facet_wrap(~taxon,
             ncol = 3,
             scales = "free")

```

### Relative Map per period

```{r regional_map, eval = T, echo = F}

relative <- regional_df %>% 
  mutate(
    period = ifelse(year %in% seq(1973,1978,1),"A_ref",
                    ifelse(year %in% seq(2020,2040,1),"AA_med",
                           ifelse(year %in% seq(2080,2100,1),"AAA_end",NA
                           )
                    )
    )
  ) %>% 
  filter(!is.na(period)) %>% 
  group_by(sub_are = as.character(sub_area),division = division, period,taxon,stock) %>% 
  summarise(per_mcp = mean(per,na.rm = T))

# Mapping

for(i in 1:length(unique(relative$stock))){

  stocks <- unique(stock_data$stock)[i]
  
reg_map <- project_shp %>% 
  left_join(relative,
             by = c("sub_are","division")
             ) %>% 
    filter(stock == stocks) %>% 
  ggplot() +
  geom_sf(
    aes(
      fill = per_mcp
    )
  ) +
  facet_wrap(~period,
             ncol = 9) +
  viridis::scale_fill_viridis() 
  
  

  name <- paste0(my_path("R","partial"),"AA_",stocks,"_regional_map_per.png")

ggsave(filename = name,
        plot = reg_map,
       width = 12)

}

```

### Relative bar per period

```{r regional_map, eval = T, echo = F}

relative_bar <- regional_df %>% 
  mutate(
    period = ifelse(year %in% seq(1973,1978,1),"A_ref",
      ifelse(year %in% seq(2020,2040,1),"AA_med",
                           ifelse(year %in% seq(2080,2100,1),"AAA_end",
                                  NA
                           )
                    )
    )
  ) %>% 
  filter(!is.na(period)) %>% 
  group_by(sub_are = as.character(sub_area),division = division, period,taxon,stock) %>% 
  summarise(per_mcp = mean(per,na.rm = T))
  mutate(per_mcp = ifelse(per_mcp > 50,50,per_mcp))


relative_bar %>% 
  ggplot() +
  geom_bar(
    aes(
      x = sub_div,
      y = period,
      fill = per_mcp
    ),
    stat = "identity"
  ) +
  facet_wrap(~stock,
             ncol = 9) +
  viridis::scale_fill_viridis()

```


### Proportion per period

```{r regional_map, eval = T, echo = F}

period_prop <- regional_df %>% 
  mutate(
    period = ifelse(year %in% seq(1973,1978,1),"A_reference",
      ifelse(year %in% seq(2020,2040,1),"AA_med",
                           ifelse(year %in% seq(2080,2100,1),"AAA_end",
                                  NA
                           )
                    )
    )
  ) %>% 
  filter(!is.na(period)) %>% 
  group_by(sub_area,division, period,taxon) %>% 
  summarise(mean_prop = mean(per,na.rm = T)) %>% 
  mutate(sub_are = as.character(sub_area))



reg_map <- project_shp %>% 
  left_join(period_prop,
            by = c("sub_are","division")) %>% 
  filter(!is.na(taxon)) %>% 
  ggplot() +
  geom_sf(
    aes(
      fill = log10(mean_prop)
    )
  ) +
  facet_wrap(~taxon+period,
             ncol = 6) +
  viridis::scale_fill_viridis()


ggsave(my_path("R","partial","regional_map_prop_log.png"),
       reg_map,
       width = 12)

```

### Relative change Mapping

```{r regional_map, eval = T, echo = F}

relative_chng <-
  regional_df %>% 
  mutate(
    period = ifelse(year %in% seq(1973,1978,1),"A_ref",
                    ifelse( year %in% seq(2020,2040,1),"AA_med",
                           ifelse(year %in% seq(2080,2100,1),"AAA_end",
                                  NA
                           )
                    )
    )
  ) %>% 
  filter(!is.na(period)) %>% 
  group_by(sub_area,division, period,stock) %>% 
  summarise(mean_mcp = mean(per,na.rm = T)) %>% 
  spread(period,mean_mcp) %>% 
  gather("fut_period","future_mcp",AA_med,AAA_end) %>% 
  # View()
  mutate(per_chg = ifelse(A_ref == 0 & future_mcp == 0, 0, # If for no change than 0
                        ifelse(A_ref == 0 & future_mcp > 0, 100, # If changes from 0 to anything then 100
                               # NA
                               ((future_mcp-A_ref)/((future_mcp+A_ref)/2))*100 # Estimate percentage change
                        )
            ),
         plot_per_change = ifelse(per_chg > 100,100,
                                  ifelse(per_chg < -100,-100,
                                  per_chg)
         ),
         sub_are = as.character(sub_area)
         )


for(i in 1:length(unique(relative$stock))){

  stocks <- unique(stock_data$stock)[i]


reg_map_diff <- project_shp %>% 
  left_join(relative_chng,
            by = c("sub_are","division")) %>% 
  filter(!is.na(stock),
         stock == stocks) %>% 
  ggplot() +
  geom_sf(
    aes(
      fill = plot_per_change
    )
  ) +
   facet_wrap(~fut_period,
             ncol = 9) +
  scale_fill_gradient2() +
  scale_color_gradient2()


  name <- paste0(my_path("R","partial"),"A_",stocks,"_regional_map_diff.png")

ggsave(filename = name,
        plot = reg_map_diff,
       width = 12)

}

```
