---
title: "Climate change will outdate the European Union fishereis quota allocation"
author: "Alex Tidd, <sup>1</sup> Elena Ojea <sup>1</sup>, Juliano Palacios-Abrantes<sup>2</sup>, William W. L. Cheung ?, U. Rashid Sumaila ?"
date: `r date()`
# output: html_notebook
---

```{r setup, include=FALSE, results = 'hide'}

#### READ ME !!! ####
library(MyFunctions)

#### Library ####
packages <- c(
  # "readxl", # Read dataframe
  # "data.table", # Read dataframe (Fast!)
  # "wesanderson",
  "tidyverse", # for all data wrangling and ggplot
  "here",
  "janitor",#, # for data cleaning
  # "tidytext", # to order the facet wrap https://juliasilge.com/blog/reorder-within/
  # "cowplot", # for figures 1 and 3
  # "ggimage", #for reading images to the circular plot
  # "ggrepel", # for nice plot labels
  # "ggsflabel", # for nice sf_plots labels
  # "spdep", # for poly2nb old
  "sf", #Spatial analysis
  "sp", #Spatial analysis
  # "purrr",#Spatial analysis
  # "rgdal", #Spatial analysis
  "tools", #Spatial analysis
  # "parallel", # for parallelization
  # "taxize", # For getting species names
  # "rfishbase", # for species ecosystem affinity
  # "zoo", #for runing mean
  # "pgirmess" # for dune test after kurtis wallas
  "knitr"
)

my_lib(packages)

# data_path <- "../data"
data_path <- my_path("D")
```

# Methods

## Species selection

In here we take the EU list of species and filter out those that we have data for to project under climate change.

Our analysis included 79.48% (n = 62) of the taxa reported at the species level by the European Union (n = 78).

```{r species_selection, eval = F, echo = F}

# -------------------- #
# Data needed
# -------------------- #

# Load EU species list
Eu_spp_list <- my_path("D","Species", name = "eu_species.csv", read = T) %>% 
# Eu_spp_list <- read.csv(here("data/species/eu_species.csv")) %>% 
  clean_names() %>% 
  rename(taxon_name = scientific_name) %>% 
  select(-common_name)

# Load SAU species list
Sau_spp_list <- my_path("D","Species", name = "exploited_species_list.csv", read = T) %>% 
# Sau_spp_list <- read.csv(here("data/species/exploited_species_list.csv")) %>% 
  clean_names()

# -------------------- #
# Get Species lists
# -------------------- #

# Get species list to analyze (n = 62)
Project_spp <- Eu_spp_list %>% 
  left_join(Sau_spp_list,
            by = "taxon_name") %>% 
  filter(!is.na(taxon_key))

# Save data for future
# write_csv(Project_spp,
#           "../data/species/species_analyzed.csv")


# Who was left out (n = 29)
Left_out_spp <- Eu_spp_list %>% 
  anti_join(Project_spp,
            by = "taxon_name")

# General categories (n = 13)
Left_out_spp %>% 
  filter(str_detect(taxon_name,"sp")) %>% 
  pull(taxon_name)


# Species left out (n = 16)
Left_out_spp %>% 
  filter(!str_detect(taxon_name,"sp")) %>% 
  pull(taxon_name)

# Numbers for methods

62/91*100 # 68.13 % of the taxon reported
62/(91-13)*100 # 79.49 % of the taxon reported at the species level


kable(Project_spp)

```

## Spatial analysis

### Crop out european region

In the following analysis we will crop out the EU region to a 0.5 x 0.5 grid

### Data for spatial
```{r spatial_data_crop, eval = F, echo = F}

## EU Shapefile

Eu_shp <- st_read(my_path("D","Spatial/ices_areas","ICES_Areas_20160601_dense.shp"))

# SAU/DBEM Gridcell
Eez_cell_id <- my_path("G","Spatial/DBEM/","EEZ_CellID.csv", read = T)

# Load Gridcell
Lon_lat_grid <- my_path("G", "Spatial/DBEM","Lon_Lat_DBEM.txt", read = T, header = F)
colnames(Lon_lat_grid) <- c("index","lon","lat")

```

### Spatial croping

```{r species_selection, eval = F, echo = F}

# Convert DBEM gridcell to sf
Grid_sf = st_as_sf(Lon_lat_grid,
            coords = c("lon", "lat")
            ) %>% 
 st_set_crs(4326) %>% # to match shapefiles
 st_transform(4326) # to match shapefiles

head(Grid_sf)

# Merge grid sf and EU sf
Eu_grid <- Eu_shp %>% 
  st_join(Grid_sf, join = st_contains) %>% 
 filter(!is.na(index)) %>%
 arrange(index) 

# Merged correctly?
# head(Eu_grid)

# Transform sf to df
Eu_grid_df <- as.data.frame(Eu_grid) %>% 
 select(index,OBJECTID:SubDivisio)


# Double check grid makes sense
Eu_grid_df %>% 
  left_join(Lon_lat_grid) %>% 
  ggplot() +
  geom_tile(aes(
    x = lon,
    y = lat,
    fill = as.factor(Division),
    color = as.factor(Division)
  )
  )

# Save data
# write_csv(Eu_grid_df,
#           "eu_grid.csv")

### TO show in notebook

my_path("D","Spatial","eu_grid.csv", read = T) %>% 
  left_join(Lon_lat_grid) %>% 
  ggplot() +
  geom_tile(aes(
    x = lon,
    y = lat,
    fill = as.factor(division),
    color = as.factor(division)
  )
  )


```


## Computing analysis

Right now doing analysis at the species level

### Read DBEM data

```{r dbem_data, eval = T, echo = T}


eu_grid <- my_path("D","Spatial","eu_grid.csv", read = T)

read_dbem <- function(taxon){
  
  file_name <- paste0(taxon,"MCP.RData")
  read_me <- my_path("G","DBEM/C6GFDL85F1_5_t2", name = file_name)
  
  if(file.exists(read_me) == F){
    data <- data.frame()
  }else{
    
    load(read_me)
    
    colnames(sppMCPfnl) <- seq(1951,2100,1)
    
    data <- sppMCPfnl %>% 
      as.data.frame() %>% 
      rowid_to_column("index") %>% 
      gather("year","mcp",2:151) %>% 
      mutate(taxon = taxon) %>% 
      filter(index %in% eu_grid$index)
  }
  
  return(data)
  
}

```


### Estimate changes

#### Temporal changes

```{r}

spp_data <- read_dbem(taxon = Project_spp$taxon_key[1])
  
  
dt <- spp_data %>%
  left_join(eu_grid) %>% 
  group_by(division,year,taxon) %>% 
  summarise(div_mcp = sum(mcp, na.rm= T)) %>% 
  mutate(
    period = ifelse(year %in% seq(1951,2000,1),"A_early",
                    ifelse(year %in% seq(2040,2060,1),"AA_med",
                           ifelse(year %in% seq(2080,2100,1),"AAA_end",
                                  NA
                           )
                    )
    )
  ) %>% 
  filter(!is.na(period)) %>% 
  group_by(division,taxon, period) %>% 
  summarise(mean_mcp = mean(div_mcp,na.rm = T)) %>% 
  spread(period,mean_mcp) %>% 
  gather("future","mcp",AA_med:AAA_end) %>% 
  mutate(per_chg = ifelse(A_early == 0 & mcp == 0, 0, # If for no change than 0
                        ifelse(A_early == 0 & mcp > 0, 100, # If changes from 0 to anything then 100
                               # NA
                               ((mcp-A_early)/((mcp+A_early)/2))*100 # Estimate percentage change
                        )
            ),
         plot_per_change = ifelse(per_chg > 100,100,
                                  ifelse(per_chg < -100,-100,
                                  per_chg)
         )
         )


head(dt,20) %>% 
kable()

```

#### Regional Estimations

```{r}

spp_data

total_spp <- spp_data %>% 
  group_by(year,taxon) %>% 
  summarise(total_mcp = sum(mcp,na.rm=T))
  
  
dt <- spp_data %>%
  left_join(eu_grid) %>% 
  group_by(year,taxon,division) %>% 
  summarise(div_mcp = sum(mcp, na.rm= T)) %>% 
  left_join(total_spp) %>% 
  mutate(
    per = (div_mcp/total_mcp)*100
  ) %>% 
 # checking
  # group_by(year) %>% 
  # summarise(sum(per))
  mutate(
    period = ifelse(year %in% seq(1951,2000,1),"A_early",
                    ifelse(year %in% seq(2040,2060,1),"AA_med",
                           ifelse(year %in% seq(2080,2100,1),"AAA_end",
                                  NA
                           )
                    )
    )
  ) %>% 
  filter(!is.na(period)) %>% 
  group_by(division,taxon, period) %>% 
  summarise(mean_mcp = mean(per,na.rm = T)) %>% 
  spread(period,mean_mcp) %>% 
  gather("future","mcp",AA_med:AAA_end) %>% 
  mutate(per_chg = ifelse(A_early == 0 & mcp == 0, 0, # If for no change than 0
                        ifelse(A_early == 0 & mcp > 0, 100, # If changes from 0 to anything then 100
                               # NA
                               ((mcp-A_early)/((mcp+A_early)/2))*100 # Estimate percentage change
                        )
            ),
         plot_per_change = ifelse(per_chg > 100,100,
                                  ifelse(per_chg < -100,-100,
                                  per_chg)
         )
         )


head(dt,20) %>% 
kable()

```

# Results

```{r}

dt %>% 
  left_join(eu_grid) %>% 
  left_join(Lon_lat_grid) %>% 
  ggplot() + 
  geom_tile(
    aes(
      x = lon,
      y = lat,
      fill = mcp,
      color = mcp
    )
  ) +
  facet_wrap(~future, ncol = 1)


# Eu_shp %>% 
#   clean_names() %>% 
#   left_join(dt,
#             by = "division") %>% 
#   ggplot() + 
#   geom_sf(aes(fill = mcp)) +
#   facet_wrap(~future, ncol = 1)


```

